Continuations via Negative Information Flow

### 2012-02-14 dual.tex
added composition and eps_fst
semantics fix

\item
Operational Semantics.
%subcode{opsem} include main
% D[P| (R v) eps| F]      &|-->&  D{dagger}[F | eps (L (-v))| P]

@@

@@

@@

\item {{(-b1) * b2}} is not the same as {{b1 * (-b2)}} as there is no
  isomorphism to translate from one to the other.

\item {{-(b1 * b2)}} is not the same as {{b1 * b2}} and is also not
  the same as {{(-b1) * (-b2)}} as there is no isomorphism that goes
  from one to the other.

\item {{-(-b)}} is not the same as {{b}} as there is no isomorphism
  that goes from one to the other.

@@

>>>>

\item
Operational Semantics.
%subcode{opsem} include main
% D[P| (R v) eps| F]      &|-->&  D{dagger}[F | eps (L (-v))| P]
% D[P| (L (-v)) eps| F]      &|-->&  D{dagger}[F | eps (R v)| P]

@@

This is also equivalent to sequencing both the computation blocks.

\begin{center}
  \includegraphics{diagrams/compose2.pdf}
\end{center}

@@

Double Negation

{{b <-> -(-b)}}

\begin{center}
  \includegraphics{diagrams/double_neg.pdf}
\end{center}

Negation distributes over {{+}}.

{{-(b1 + b2) <-> (b1) + (-b2)}}

\begin{center}
  \includegraphics{diagrams/dist_neg_plus.pdf}
\end{center}

{{eps_{fst} }}

{{(-b1)*b2 + b1*b2 <-> 0}}

\begin{center}
  \includegraphics{diagrams/eps_fst.pdf}
\end{center}

Lifting negation out of {{*}}.

{{(-b1) * b2 <-> -(b1 * b2) <-> b1 * (-b2)}}

\begin{center}
  \includegraphics{diagrams/mult_neg.pdf}
\end{center}

The following isomoprhism can be constructed similarly

{{b1 * b2 <-> (-b1)*(-b2)}}

@@

@@

\item Can the operational semantics for {{langRevEE}} be an
  interpreter that is implemented in {{langRevT}} (similar to how the
  the tree traversal interpreter was implemented). This would imply
  the existence of a more powerful construction than Int, wherein the
  products would also be preserved. This is possibly worth a paper in
  itself.
